Speed and strength of an epidemic intervention

### 2020-10-01 doc/speedstrength.tex
Working on revisions

There has been a great deal of discussion of the importance of pre-symptomatic  transmission of COVID-19. Pre-symptomatic transmission is likely to be hard to detect, and therefore hard to prevent. Thus, it might be supposed that an increase in the estimated importance of pre-symptomatic transmission would lead to an increase in the estimated difficulty

>>>>

There has been a great deal of discussion of the importance of pre-symptomatic  transmission of COVID-19. Pre-symptomatic transmission is likely to be hard to detect, and therefore hard to prevent. Thus, it might be supposed that an increase in the estimated importance of pre-symptomatic transmission would lead to an increase in the estimated difficulty.

A generation-interval perspective can be used to challenge this view. More early transmission, for a given value of \rr, means less transmission per individual -- that is, a lower value of \RR. Thus, although earlier transmission could make intervention less effective, it also means that less intervention may be necessary.

Given sufficient assumptions, a strength-based calculation could provide an answer for any particular scenario. But using the speed-based paradigm substantially clarifies the situation. As with the HIV example, our estimate of the speed of the epidemic is not changed by information about timing of transmission. Thus, the question is reduced to whether (and how) we expect pre-symptomatic transmission to affect the effective speed of intervention.

Case detection is based on contact tracing, testing and symptoms. Thus, we don't expect pre-symptomatic infection to change the intervention hazard $h$. The effective speed, however, is a (sort-of) mean taken over the (backwards) generation interval. If the
